\begin{center}
\LARGE{A Tool for Checking Correctness of Design Diagrams in UML}
\end{center}

\vspace{10pt}

\noindent
Author: Bc. Ivo Dlouhý, xdlouh05@stud.fit.vutbr.cz \\
Faculty of Information Technology, Brno University of Technology \\

\noindent\rule{16cm}{0.4pt}

\vspace{7pt}

\section{Visual Paradigm Plugin}
The Visual Paradigm plugin uses the Ant build system.
\begin{enumerate}
  \item Navigate to the umllint-vp/src directory and start Ant
  \item Ant compiles the plugin and creates a umllint-vp/src/plugin directory that the 
  \item Copy the files in plugin directory into the plugins/net.umllint.plugin.vp/ directory of your Visual Paradigm
  \item Set up a writeable temporary directory in the umlllint.properties file
\end{enumerate}

\section{Command Line Tool}
The command line tool uses the Ant build system.
\begin{enumerate}
  \item Navigate to the umllint-tool/src directory and start Ant
  \item Ant compiles the plugin and creates a umllint-tool/build/artifacts/jar that holds the umllint-tool.jar and other
\end{enumerate}

\section{Master's Thesis}
The thesis uses a makefile system
\begin{enumerate}
  \item Navigate to the umllint-thesis/src and start make.
  \item The result is in the dp-dlouhy.pdf file.
\end{enumerate}

\section{Server}
The Server component uses the Gradle build system.
\begin{enumerate}
  \item Setup the connection string, user and password to the database in the local or production.properties file
  \item Navigate to the umllint-server and call ./gradlew war to generate the WAR file
  \item Upload WAR from the build/libs directory to the web server
\end{enumerate}

\section{Database}
The Database drop and create scripts are located in the umllint-server/database directory.
\begin{enumerate}
  \item Connect to the database server and run the scripts.
\end{enumerate}